\section{Assessment criteria}
\label{sec:criteria}

The result of the literature review conducted in \autoref{sec:criteria-selection} was a selection of seven papers. Six of these \parencite{Rosenfeldt_2000,Jha_2014,Lin_2012,Davidson_2012,Cuschieri_2019,Katz_2006} are guides for academic writing, providing a source of guidelines that the articles could be compared against. The remaining paper \parencite{Martenson_2016} is a guide for how to evaluate academic papers. While primarily targeted towards reviewers, especially peer reviewers, the article still provide ways to evaluate the selected papers, especially because it gives an idea of what peer reviewers are supposed to look for when evaluating papers.

The guides were searched for recommendations related to research questions. These were then combined to create a set of assessment criteria for the selected papers. These criteria are listed in \autoref{tab:criteria}, alongside the sources they are based on. As the criteria are based on guides for both writing and evaluating academic papers, these make a nice, well-rounded framework for evaluating whether the selected articles present and use research questions the way they should.

The selected topic for this paper revolves around the actual structure of the selected papers, rather than the methodology used in the papers. As such, the same assessment criteria are used for papers using both quantitative and qualitative methods.

\begin{table*}[ht]
    \centering
    \begin{tabular}{p{0.5\textwidth} p{0.4\textwidth}}
        \textbf{Research questions} \\
        \hline
        Does the paper contain one or more research questions or hypotheses? & \cite{Rosenfeldt_2000,Jha_2014,Lin_2012,Davidson_2012,Cuschieri_2019,Katz_2006,Martenson_2016} \\
        How are the research question(s) presented? & \cite{Rosenfeldt_2000,Jha_2014,Lin_2012,Davidson_2012,Cuschieri_2019,Katz_2006} \\
        \\
        
        \textbf{Structure} \\
        \hline
        Where in the paper are the research question(s) introduced? & \cite{Rosenfeldt_2000,Jha_2014,Lin_2012,Davidson_2012,Cuschieri_2019,Katz_2006} \\
        How do the results presented in the paper answer the research question(s)? & \cite{Jha_2014,Davidson_2012,Cuschieri_2019,Katz_2006,Martenson_2016} \\
        How do the conclusions drawn in the paper connect with the research question(s) presented? & \cite{Davidson_2012,Katz_2006,Martenson_2016} \\
    \end{tabular}
    \caption{Assessment criteria for the selected papers}
    \label{tab:criteria}
\end{table*}